Synpotic Soil Characterization

### 2023-03-29 3-reports/characterization_report.Rmd
report: figures for manuscript

>>>>

### figures for manuscript

```{r ms_mehlich, fig.height=5, fig.width=6}
tar_read(gg_by_transect_colorsites)$gg_wle_mehlich
```

```{r ms_wle_icp, fig.height=9, fig.width=9}
tar_read(gg_by_transect_colorsites)$gg_wle_icp
```

```{r ms_cb_icp, fig.height=9, fig.width=9}
tar_read(gg_by_transect_colorsites)$gg_cb_icp
```

```{r ms_wle_anions, fig.height=5, fig.width=9}
tar_read(gg_by_transect_colorsites)$gg_wle_anions
```

```{r ms_cb_anions, fig.height=5, fig.width=9}
tar_read(gg_by_transect_colorsites)$gg_cb_anions
```

```{r ms_cb_fe, fig.height=5, fig.width=6}
tar_read(gg_by_transect_colorsites)$gg_cb_fe
```

```{r ms_cb_cond, fig.height=5, fig.width=6}
tar_read(gg_by_transect_colorsites)$gg_cb_spcond
```
